Trap spaces of Boolean networks are conflict-free siphons of their Petri net encoding

### 2023-02-18 manuscripts/TCS2022/tcs2022.tex
experimental analysis on random models

First, \dots

Second, \dots

Third, \dots

>>>>

First, \texttt{mpbn} did not be able to handle any model because all the models are non-locally-monotonic.
Recall that a Boolean network is non-locally-monotonic if only one of its Boolean functions is non-locally-monotonic.
Hence, it is apparent that all the randomly generated models are non-locally-monotonic.
This observation confirms the limit on the applicable model class of \texttt{mpbn}.

Second, surprisingly \texttt{bioLQM} could not handle any model.
One of the reason may be that the BDD characterizing all trap spaces is too large, and its computation is slow.
It is apparent because the network size is large (\(\geq 100\)) and the Boolean functions are not simple.

Third, \texttt{PyBoolNet} could handle every model of network size less than or equal to 300.
It only failed in one model of network size 350 but 29 models of network size 400.
The average running time vastly increases as the network size increases.
As compared to the four methods of our approach, the performance of \texttt{PyBoolNet} is comparable for the 100-node and 200-node models.
However, from \(n = 250\), the performance difference is exhibited more clearly.
